---
title: "R-Tips Notebook"
output:
  html_document:
    df_print: paged
---

##Useful Links

*  [R for Data Science](https://r4ds.had.co.nz/)
*  [Definitive Guide to Notebooks/Markdown](https://bookdown.org/yihui/rmarkdown/markdown-syntax.html) 
*  [knitr options](http://yihui.name/knitr/options/)
*  [R Markdown Templates](https://github.com/dr-harper/example-rmd-templates)
*  [Github with Rstudio](http://happygitwithr.com/rstudio-git-github.html)
*  [papaja](https://crsh.github.io/papaja_man/index.html)


##Example

First, load in all necessary packages as well as the data.  

```{r Libraries, message=F}
  #section 2.6.1 of Definitive Guide
library(lavaan)
library(tidyverse) #managing data
library(broom) #cleaning output
library(semPlot) #creating path diagrams
library(sjPlot) #for plotting things
df<-read.csv("ECLSK2011 PSYC 501.csv")
```

We will be using an example right from class. Examining a quadratic growth model.  

```{r Quadratic Growth}
gc.q.math<-"
i=~ 1*x2_math + 1*x4_math + 1*x6_math + 1*x7_math + 1*x8_math
sl=~ 0*x2_math + 1*x4_math + 2*x6_math + 3*x7_math + 4*x8_math
sq=~ 0*x2_math + 1*x4_math + 4*x6_math + 9*x7_math + 16*x8_math
"
gc.q.math.fit<-growth(gc.q.math,data=df, missing="fiml")
summary(gc.q.math.fit, fit.measures=T, standardized=T)
```



The output can be somewhat difficult to manage. That is where the `broom` package comes into play using the `tidy()` function. 


```{r Tidy quadratic growth}

tidygrow <- tidy(gc.q.math.fit)
#View(tidygrow)

#Create df to reflect just estimates
est <- tidygrow %>%
  filter(std.error>0) %>%
  filter(!grepl('math', term)) %>% #removes all terms that have 'math' in the name
  filter(!grepl('~~',term)) %>% #this is the line that evaluates the op variable
  select(term, estimate, std.error, p.value, std.all)

#create df to reflect only variance
var <- tidygrow %>%
  filter(std.error>0) %>%
  filter(!grepl('math', term)) %>%
  filter(grepl('~~', term)) %>%
  select(term, estimate, std.error, p.value, std.all) %>%
  slice(1:3) #only want the variance

#Combine dataframes
res.qg <- bind_cols(est,var) %>%
  select(term, estimate, std.error, std.all, p.value, estimate1, p.value1)

rownames(res.qg) <- c('Intercept','Linear Slope','Quadratic Slope')

#rounding the estimates
res.qg$estimate <- round(res.qg$estimate, 3)
res.qg$std.error <- round(res.qg$std.error, 3)
res.qg$std.all <- round(res.qg$std.all, 3)
res.qg$estimate1 <- round(res.qg$estimate1, 3)

res.qg <- rownames_to_column(res.qg) %>%
  select(rowname, estimate, std.error, std.all, p.value, estimate1, p.value1)

names(res.qg) <- c('', 'Estimate', 'Std. Error', 'Std. Est.', 'p-value', 
                   'Variance','p-value')
tab_df(res.qg, title='Quadratic Parameter Estimates',
       file='QuadParam.html')

```


```{r}
quad <- as.data.frame(fitmeasures(gc.q.math.fit, c("cfi","srmr","rmsea")))
names(quad)[1]<-"Quadratic Growth"
quad$index <- NA
quad[1,2]<-"CFI"
quad[2,2]<-"SRMR"
quad[3,2]<-"RMSEA"
quad[4,2]<-"AIC"
quad[4,1]<-AIC(gc.q.math.fit)
quad[5,2]<-"BIC"
quad[5,1]<-BIC(gc.q.math.fit)
quad$`Quadratic Growth` <- round(quad$`Quadratic Growth`,3)

tab_df(quad, title='Quadratic Growth Fit Stats', 
       file = 'QuadFit.html')
```


This part gets a little overwhelming and can be difficult. What if we just make a function to do it for us??? 

```{r function}
fit_stats <- function(model, varname){
  modelframe <- as.data.frame(fitmeasures(model, c("cfi","srmr","rmsea")))
names(modelframe)[1]<-'varname'
modelframe$index <- NA
modelframe[1,2]<-"CFI"
modelframe[2,2]<-"SRMR"
modelframe[3,2]<-"RMSEA"
modelframe[4,2]<-"AIC"
modelframe[4,1]<-AIC(model)
modelframe[5,2]<-"BIC"
modelframe[5,1]<-BIC(model)
modelframe$varname <- round(modelframe$varname,3)
return(modelframe)
}

fit_stats(gc.q.math.fit, 'quadgrow')

```

  
***  
###Sample Text with Code 
  
Here we can also begin to integrate some of the R code into our text. Example: 

The model showed good fit based on most fit measures (CFI = `r round(fitmeasures(gc.q.math.fit, 'cfi'),3)`, RMSEA = `r round(fitmeasures(gc.q.math.fit, 'srmr'),3)` and SRMR = `r round(fitmeasures(gc.q.math.fit, 'rmsea'),3)`). 

THe reall awesome thing about this is that they are dynamic. If we were to run analyses again, and include another variable in the model, these values would update accourdingly! 

###Correlation Table

Now we know that it is always good to include a correlation table into our manuscripts. But we often forget them until the final piece because we don't want to have to transfer everything over! Who would want to do that (is that what undergrad RA's are for??)

This is now a thing of the past! R can do it for you. 
```{r correlation table, eval=F}

#Don't need all of the variables; only select the ones you will be using 

cor <- select(df, x1_SES:x8_wght)

#This correlation matrix is too large for the rmarkdown document. Please find it in the folder titled "correlation.html"

sjt.corr(cor,show.p = FALSE, na.deletion = 'pairwise', triangle="upper", 
           title = "Correlations",
           CSS=list(css.thead="border-top:double black; font-weight:normal; font-size:0.9em;",
         css.firsttablecol="font-weight:normal; font-size:0.9em;"),file="Correlation.html")
```



###Plots

It is always great to visualize your model. The package [semPlot](http://sachaepskamp.com/documentation/semPlot/semPaths.html) can come in very handy. Let's take a look: 

```{r semPlot}

semPaths(gc.q.math.fit, layout='tree2')

```

